Supporting Information for ``Identifying regime transitions for water governance at a basin scale''

### 2023-05-15 paper/sup/04_robustness.tex
refactor(paper): :memo: 顺一遍正文和补充材料

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified December 2018
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% FOR FIGURES, DO NOT USE \psfrag
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% IMPORTANT NOTE:
%
% SUPPORTING INFORMATION DOCUMENTATION IS NOT COPYEDITED BEFORE PUBLICATION.
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH (use for all of them)
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER
% ms    JAMES
% ef    EARTH'S FUTURE
%
%
%
% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

\documentclass[draft,wrr]{../agutexSI2019}
\usepackage{amsmath}
% For using tabularx
\usepackage{tabularx}
\usepackage{booktabs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  SUPPORTING INFORMATION TEMPLATE
%
%% ------------------------------------------------------------------------ %%
%
%
%Please use this template when formatting and submitting your Supporting Information.

%This template serves as both a “table of contents” for the supporting information for your article and as a summary of files.
%
%
%OVERVIEW
%
%Please note that all supporting information will be peer reviewed with your manuscript. It will not be copyedited if the paper is accepted.
%In general, the purpose of the supporting information is to enable authors to provide and archive auxiliary information such as data tables, method information, figures, video, or computer software, in digital formats so that other scientists can use it.
%The key criteria are that the data:
% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
%    including %data so the experiment can be reproducible);
% 2. are likely to be usable or used by other scientists working in the field;
% 3. are described with sufficient precision that other scientists can understand them, and
% 4. are not exe files.
%
%USING THIS TEMPLATE
%
%***All references should be included in the reference list of the main paper so that they can be indexed, linked, and counted as citations.  The reference section does not count toward length limits.
%
%All Supporting text and figures should be included in this document. Insert supporting information content into each appropriate section of the template. To add additional captions, simply copy and paste each sample as needed.

%Tables may be included, but can also be uploaded separately, especially if they are larger than 1 page, or if necessary for retaining table formatting. Data sets, large tables, movie files, and audio files should be uploaded separately. Include their captions in this document and list the file name with the caption. You will be prompted to upload these files on the Upload Files tab during the submission process, using file type “Supporting Information (SI)”

%IMPORTANT NOTE ON FIGURES AND TABLES
% Placeholders for figures and tables appear after the \end{article} command, after references.
% DO NOT USE \psfrag or \subfigure commands.
%
 \usepackage{graphicx}
%
%  Uncomment the following command to allow illustrations to print
%   when using Draft:
\setkeys{Gin}{draft=true}
%
% You may need to use one of these options for graphicx depending on the driver program you are using.
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
%\authorrunninghead{BALES ET AL.}

% Shorter version of title entered in capital letters:
%\titlerunninghead{SHORT TITLE}

%Corresponding author mailing address and e-mail address:
%\authoraddr{Corresponding author: A. B. Smith,
%Department of Hydrology and Water Resources, University of
%Arizona, Harshbarger Building 11, Tucson, AZ 85721, USA.
%(a.b.smith@hwr.arizona.edu)}

\begin{document}
\noindent\textbf{\large{Supplementary Information for}}

\input{../metadata.tex}
\begin{article}

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}
\item Text S1 to S3
\item Figures S1 to S3
\item Tables S1 to S2
%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}

\noindent\textbf{Introduction}
%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
% 1. a general overview of the kind of data files;
% 2. information about when and how the data were collected or created;
% 3. a general description of processing steps used;
% 4. any known imperfections or anomalies in the data.
When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale. Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
The formulation in detail for applying the SFV-index is available in the~\ref{secA2}.
We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonies them for analysis.

\noindent\textbf{YRB Regions}\label{secA1}
\input{01_yrb.tex}

% \noindent\textbf{SFV-index}\label{secA2}
% \input{02_indicator.tex}

@@

\noindent\textbf{Trend of Indicators}\label{secA2}

% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
The index of stress (SFV indicator, IS) in the study period (including three different periods) showed a change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
Among the four different regions (Figure~\ref{fig:scarcity}~B), the source region (SR) has almost no contribution to IS changes in the three periods, and the downstream region (DR) only has a weak negative contribution in the governance transforming regime and the adaptation oriented regime.
The upper and middle reaches (UR and MR) had the greatest impact on the IS changes. Wherein, the upper region (UR) made the greatest contribution during the massive supply regime and governance transforming regime, while the middle reaches made the greatest contribution in adaptation oriented regime.

% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:purpose}~A）。
% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
In terms of water use purpose indicator, IP remained basically unchanged in a massive supply regime, but showed a rapid decline in the period of governance transformation and adaptation oriented regime (Figure~\ref{fig:purpose}~A).
Throughout the three periods, the change of irrigation water dominated the change of the IP, while urban and rural water for human settlements and rural livestock had almost no influence on the change of IP (Figure~\ref{fig:allocation}~B).

% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
The water allocation (IA) showed an obvious ``V-shaped'' trend, indicating that water resources in the different regions within the YRB first gradually moved away from uniform distribution, and then gradually tended to uniform distribution since 2000 (Figure~\ref{fig:allocation}).

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/priority.jpg}
\caption{Changing trend of the indicator of purpose}\label{fig:purpose}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/allocation.png}
\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/scarcity.png}
\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
\end{figure}

By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), purpose (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.

When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.
On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI. However, the correlations of other combinations are not statistically significant overall.

The correlations between time periods are very different with the overall trend above.
There is no significant correlation between any indicator combinations in the massive supply regime (P1).
In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3). However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).

\input{../response_letter/source/tab_corr.tex}

@@

\noindent\textbf{Datasets}\label{secA3}
\input{03_datasets.tex}

%%Enter Data Set, Movie, and Audio captions here
%%EXAMPLE CAPTIONS

% \noindent\textbf{Data Set S1.} %Type or paste caption here.
%upload your dataset(s) to AGU's journal submission site and select "Supporting Information (SI)" as the file type. Following naming %convention: ds01.

%Repeat for any additional Supporting data sets

% \noindent\textbf{Movie S1.} %Type or paste caption here.
%upload your movie(s) to AGU's journal submission site and select, "Supporting Information %(SI)" as the file type. Following naming convention: ms01.

%Repeat any additional Supporting movies

% \noindent\textbf{Audio S1.} %Type or paste caption here.
%upload your audio file(s) to AGU's journal submission site and select "Supporting Information %(SI)" as the file type. Following naming convention: auds01.

%Repeat for any additional Supporting audio files

%%% End of body of article:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Notation section goes here
%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ------------------------------------------------------------------------ %%
%%  REFERENCE LIST AND TEXT CITATIONS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\bibliography{../mybibtex.bib}
\end{article}
\clearpage
\end{document}

>>>>

% 为了增强本研究的鲁棒性，我们在不同的显著性水平下检验了突变点的识别结果，发现在0.0005到0.05的置信度水平下，都只能识别出本研究发现的两个突变点（1978与2001）。
In order to enhance the robustness of this study, we tested the identification results of mutation points at different significance levels.
Our results that only two mutation points (1978 and 2001) could be identified at the confidence level of $0.0005$ to $0.05$ (Figure~\ref{fig:sensitivity}).
% 此外，我们讨论了在指标中没有体现的水库流量变化，在所有水库（图 x）中，我们分析了10个先后建成的枢纽水库，发现水库在 governance transforming regime 之后开始增强其调度的水平
In addition, we analyzed the changes of reservoir flow that are not reflected in the IWGI.\ Among all the reservoirs (Figure~\ref{fig:reservoirs}), we focused on $9$ major reservoirs built successively and find that the reservoirs began to enhance their variability after the governance transforming regime, suggesting a higher level of regulating (Figure~\ref{fig:conveyance}).

@@

@@

### 2023-05-15 paper/sup/supplementary_information.tex
fix(paper): :bug: 修改审稿意见返修的对应行号
refactor(paper): :memo: 顺一遍正文和补充材料

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}
\item Text S1 to S3
\item Figures S1 to S3
\item Tables S1 to S2
%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}

\noindent\textbf{Introduction}
%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
% 1. a general overview of the kind of data files;
% 2. information about when and how the data were collected or created;
% 3. a general description of processing steps used;
% 4. any known imperfections or anomalies in the data.
When calculating the indicators (especially the SFV water stress index and the allocation entropy metric), we should use data at a lower (regional scale in this study) spatial scale. Therefore, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.
The formulation in detail for applying the SFV-index is available in the~\ref{secA2}.
We used multiple sources of datasets in this study, \\textit{Supporting Information}~\ref{secA3} introduces where they came from and how we harmonies them for analysis.

@@

\noindent\textbf{SFV-index}\label{secA2}
\input{02_indicator.tex}

\begin{figure}[tb]
\centering
\includegraphics[width=0.6\linewidth]{sup/reservoirs.pdf}
\caption{
      Numbers of new reservoirs in each year.
}\label{fig:reservoirs}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{sup/sensitivity.pdf}
\caption{
      Sensitivity analysis of the threshold of p-values.
      \textbf{A.} number of breakpoints in different p-values, the scheme with two-breakpoints are the dominant situation.
      \textbf{B.} Threshold of p-values \(\alpha=0.0005\).
      \textbf{C.} Threshold of p-values \(\alpha=0.05\).
}\label{fig:sensitivity}
\end{figure}

% 构成稀缺情况的指标（SFV指数）在研究时段（包括三个不同时期）内呈现出先降低、然后迅速增加、最后再次略微降低的变化趋势（图~\ref{ch4:fig:scarcity}~A），表明水资源压力先减少再迅速增加，后趋于稳定。
% 源区、上游、中游、下游这四个不同的区域中（图~\ref{ch4:fig:scarcity}~B），源区对三个时段的SFV指标变化几乎没有贡献，下游也仅在治理转变时期和适应增强时期呈现微弱的负向贡献。
% 对稀缺情况影响最大的是黄河的上游和中游，上游在集中供水时期和治理转变时期都是SFV变化的最大贡献区域，中游则在适应增强时期做出最大贡献。
The index of scarcity (SFV index) in the study period (including three different periods) showed A change trend of first decreasing, then rapidly increasing, and finally slightly decreasing again (Figure~\ref{fig:scarcity}~A), indicating that water resource pressure first decreased, then rapidly increased, and then stabilized.
In the four different regions (Figure~\ref{fig:scarcity}~B), the source region has almost no contribution to SFV index changes in the three periods, and the downstream region only has a weak negative contribution in the governance transition period and the adaptation enhancement period.
The upper and middle reaches of the Yellow River had the greatest impact on the scarcity. The upper reaches made the greatest contribution to SFV change in the period of centralized water supply and governance change, while the middle reaches made the greatest contribution in the period of adaptation enhancement.

% 在用水目的上，供给性用水比例在集中供水时期基本保持不变，但在治理转变时期和适应增强时期呈现迅速下降的趋势（图\ref{ch4:fig:priority}~A）。
% 三个时段都是由灌溉用水的变化主导了该比例变化，城市、农村的人居用水、农村牲畜用水等几乎对该比例的变化没有影响（图\ref{ch4:fig:allocation}~B）。
In terms of water use purpose, the proportion of supply water remained basically unchanged in the period of centralized water supply, but showed A rapid decline in the period of governance transformation and adaptation enhancement (Figure~\ref{fig:priority}~A).
In the three periods, the change of irrigation water dominated the change of the proportion, while urban and rural water for human settlements and rural livestock had almost no influence on the change of the proportion (Figure~\ref{fig:allocation}~B).

% 分配方式的指标变化呈现明显“V形”趋势，表明黄河的源区、上游、中游、下游之间水资源呈现先逐渐远离均匀分配，又在2000年后逐渐趋于平均的变化过程（图\ref{ch4:fig:allocation}）。
The index change of distribution mode showed an obvious ``V-shaped'' trend, indicating that water resources in the source region, upper, middle and lower reaches of the Yellow River first gradually moved away from uniform distribution, and then gradually tended to average distribution after 2000 (Figure~\ref{fig:allocation}).

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/priority.jpg}
\caption{Changing trend of the indicator of priority}\label{fig:priority}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/allocation.png}
\caption{Changing trend of the indicator of allocation}\label{fig:allocation}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{sup/scarcity.png}
\caption{Changing trend of the indicator of stress}\label{fig:scarcity}
\end{figure}

By analyzing the correlation of the integrated management index (IWGI) and its three sub-indexes: stress (IS), priority (IP) and allocation (IA) in three different periods, namely, the massive supply regime (P1: $1965 \sim 1978$), governance transforming regime (P2: $1979 \sim 2001$) and adaptation oriented regime (P3: $2002 \sim 2013$), the following results are obtained.

When we focus on the correlation from P1 to P3, the results show significant negative correlation between IS and IP (correlation coefficient is $r = -0.75$, $p < 0.01$), indicating that there is a strong negative relationship between IS and IP.
On the other hand, there is a significant positive correlation between IA and IWGI (correlation coefficients are $r = 0.75$, $p < 0.01$), indicating a positive relationship between IA and IWGI. However, the correlations of other combinations are not statistically significant overall.

The correlations between time periods are very different with the overall trend above.
There is no significant correlation between any indicator combinations in the massive supply regime (P1).
In the governance transforming regime (P2), there is a significant negative correlation between IS and IP (correlation coefficient $r = -0.90$, $p < 0.01$), a significant negative correlation between IS and IA (correlation coefficient $r = -0.87$, $p < 0.01$), and a significant positive correlation between IP and IA (correlation coefficient $r = 0.77$, $p < 0.01$).
The correlations between IS and IP, IS and IA, and IS and IWGI were not statistically significant in the adaptation oriented regime (P3). However, there is a significant negative correlation between IP and IA (correlation coefficients are $r = -0.86$, $p < 0.01$).

\input{../response_letter/source/tab_corr.tex}

\noindent\textbf{Datasets}\label{secA3}
\input{03_datasets.tex}

>>>>

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}
\item Text S1 to S3
\item Figures S1 to Figure~\ref{fig:conveyance}
%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}

\noindent\textbf{Introduction}
%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
% 1. a general overview of the kind of data files;
% 2. information about when and how the data were collected or created;
% 3. a general description of processing steps used;
% 4. any known imperfections or anomalies in the data.
Section~\ref{secA1} provides a brief introduction to four regions (Source Region, Upper Region, Middle Region, and Lower Region -SR, UR, MR, and LR) of the YRB.\
Section~\ref{secA2} detailed explains the changing trend of three indicators.
Section~\ref{secA3} describes the correlations between the three indicators and
Section~\ref{secA4} provides some sensitivity analysis for testing robustness.

% Based on vary characteristics, we divide the YRB into four regions: source region (SR), upper region (UR), middle region (MR), and lower region (LR), according to characteristics and customary practices in the~\ref{secA1}.

@@

\noindent\textbf{Trend of Indicators}\label{secA2}
\input{02_indicator.tex}

\noindent\textbf{Correlation of Indicators}\label{secA3}
\input{03_correlation.tex}

\noindent\textbf{Robustness}\label{secA4}
\input{04_robustness.tex}

% \noindent\textbf{Datasets}\label{secA3}
% \input{03_datasets.tex}
